Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-19 providence/sections/intro.tex
VA 2020 ---> 2016

\subsubsection{Organization} 
Sections \ref{sec:model} provides preliminaries on the \BRAVO and \Minerva audits. Section \ref{sec:prov} describes the \Providence audit, section \ref{sec:sims} the simulations comparing the number of ballots drawn using various ballot polling audits and section \ref{sec:pilot} the use of \Providence in an audit carried out by the Board of Elections of Rhode Island. Section \ref{sec:workload} presents our workload model and describes its use for a ballot polling audit using details of the 2020 US Presidential election in the state of Virginia. Our conclusions, the availability of an audit implementation and acknowledgements may be found in sections \ref{sec:conc}, \ref{sec:avail} and \ref{sec:ack} respectively.

>>>>

\subsubsection{Organization} 
Sections \ref{sec:model} provides preliminaries on the \BRAVO and \Minerva audits. Section \ref{sec:prov} describes the \Providence audit, section \ref{sec:sims} the simulations comparing the number of ballots drawn using various ballot polling audits and section \ref{sec:pilot} the use of \Providence in an audit carried out by the Board of Elections of Rhode Island. Section \ref{sec:workload} presents our workload model and describes its use for a ballot polling audit using details of the 2016 US Presidential election in the state of Virginia. Our conclusions, the availability of an audit implementation and acknowledgements may be found in sections \ref{sec:conc}, \ref{sec:avail} and \ref{sec:ack} respectively.

### 2023-02-19 providence/sections/workload.tex
VA 2020 ---> 2016

Figure~\ref{fig:avg_bals_ratio} provides the same number as a fraction of the \Providence values.
It is straightforward to show that \Providence and both forms of \BRAVO collapse to the same test when each round corresponds to a single ballot. Figures~\ref{fig:avg_bals} and \ref{fig:avg_bals_ratio} show that for larger stopping probabilities $p$ (i.e. larger rounds), \Providence requires fewer ballots on average. In particular, the savings of \Providence become larger as $p$ increases; for $p=0.95$, EoR \BRAVO and SO \BRAVO require more than $2$ and $1.4$ times as many ballots as \Providence respectively. 
\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{avg_bals_ratio.png}
%\includegraphics[width=.5\textwidth]{avg_bals_ratio_errorbars.png}
%\includegraphics[width=.5\textwidth]{avg_bals_ratio_errorbars.png}
\includegraphics[width=.5\textwidth]{avg_bals_ratio_quantiles.png}
\caption{The total number of ballots sampled on average, as a fraction of those sampled by \Providence, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2020 US Presidential election in the state of Virginia. The $0.25$ and $0.75$ quantiles are shown as in Figure~\ref{fig:avg_bals}.}
\label{fig:avg_bals_ratio}
\end{figure}

>>>>

Figure~\ref{fig:avg_bals_ratio} provides the same number as a fraction of the \Providence values.
It is straightforward to show that \Providence and both forms of \BRAVO collapse to the same test when each round corresponds to a single ballot. Figures~\ref{fig:avg_bals} and \ref{fig:avg_bals_ratio} show that for larger stopping probabilities $p$ (i.e. larger rounds), \Providence requires fewer ballots on average. In particular, the savings of \Providence become larger as $p$ increases; for $p=0.95$, EoR \BRAVO and SO \BRAVO require more than $2$ and $1.4$ times as many ballots as \Providence respectively. 
\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{avg_bals_ratio.png}
%\includegraphics[width=.5\textwidth]{avg_bals_ratio_errorbars.png}
%\includegraphics[width=.5\textwidth]{avg_bals_ratio_errorbars.png}
\includegraphics[width=.5\textwidth]{avg_bals_ratio_quantiles.png}
\caption{The total number of ballots sampled on average, as a fraction of those sampled by \Providence, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2016 US Presidential election in the state of Virginia. The $0.25$ and $0.75$ quantiles are shown as in Figure~\ref{fig:avg_bals}.}
\label{fig:avg_bals_ratio}
\end{figure}
